Estimation of the perceived time of presence of sources in urban acoustic environments using deep learning techniques

### 2019-06-19 paper/submitted/gontierAa2019.tex
submitted version

\usepackage[latin9]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

@@

\bibliographystyle{unsrt}
\bibliography{refs}

>>>>

\usepackage[latin9]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\graphicspath{{figures/}{./}}

@@

\begin{thebibliography}{10}

\bibitem{ec2002}
EC.
\newblock Directive 2002/49/{EC} of the {E}uropean {P}arliament and of the
  {C}ouncil of 25 june 2002 relating to the assessment and management of
  environmental noise.
\newblock {\em Off. J. Eur. Communities}, 189:12, 2002.

\bibitem{iso2014}
{ISO 12913-1:2014}.
\newblock Acoustics - soundscape - part 1: definition and conceptual framework.
\newblock Standard, International Organization for Standardization, Geneva, CH,
  2014.

\bibitem{viollon2000}
S.~Viollon and C.~Lavandier.
\newblock Multidimensional assessment of the acoustic quality of urban
  environments.
\newblock In {\em INTER-NOISE 2000}, 2000.

\bibitem{axelsson2010}
O.~Axelsson, M.E. Nilsson, and B.~Berglund.
\newblock A principal components model of soundscape perception.
\newblock {\em J. Ac. Soc. Am.}, 128:2836, 2010.

\bibitem{cain2013}
R.~Cain, P.~Jennings, and J.~Poxon.
\newblock The development and application of the emotional dimensions of a
  soundscape.
\newblock {\em Applied Acoustics}, 74:232--239, 2013.

\bibitem{jeon2018}
J.Y. Jeon, J.Y. Hong, C.~Lavandier, J.~Lafon, O.~Axelsson, and M.~Hurtig.
\newblock A cross-national comparison in assessment of urban park soundscapes
  in {F}rance, {K}orea, and {S}weden through laboratory experiments.
\newblock {\em Applied Acoustics}, 133:107--117, 2018.

\bibitem{aletta2016}
F.~Aletta, J.~Kang, and O.~Axelsson.
\newblock Soundscape descriptors and a conceptual framework for developing
  predictive soundscape models.
\newblock {\em Landsc. Urban Plan.}, 149:65--74, 2016.

\bibitem{aumond2017}
P.~Aumond, A.~Can, B.~De Coensel, D.~Botteldooren, C.~Ribeiro, and
  C.~Lavandier.
\newblock Modeling soundscape pleasantness using perceptive assessments and
  acoustic measurements along paths in urban context.
\newblock {\em Acta Acust. unit. Acust.}, 103:430--443, 2017.

\bibitem{delaitre2014}
P.~Delaitre, C.~Lavandier, C.~Ribeiro, M.~Quoy, E.~D'Hondt, E.~Gonzalez Boix,
  and K.~Kambona.
\newblock Influence of loudness of noise events on perceived sound quality in
  urban context.
\newblock In {\em Inter Noise}, 2014.

\bibitem{blauert1997}
J.~Blauert and U.~Jekosch.
\newblock Sound quality evaluation: a multi layered problem.
\newblock {\em Acta Acust. unit. Acust.}, 83:747--53, 1997.

\bibitem{jekosch2004}
U.~Jekosch.
\newblock Basic concepts and terms quality, reconsidered in the context of
  product-sound quality.
\newblock {\em Acta Acust. unit. Acust.}, 90:999--1006, 2004.

\bibitem{nilsson2007}
M.E. Nilsson, D.~Botteldooren, and B.~De Coensel.
\newblock Acoustic indicators of soundscape quality and noise annoyance in
  outdoor urban areas.
\newblock In {\em 19th International Congress on Acoustics}, 2007.

\bibitem{perez2012}
I.~Garc\'ia P\'erez, I.~Aspuru Soloaga, K.~Herranz-Pascual, and
  I.~Garc\'ia-Borreguero.
\newblock Validation of an indicator for the assessment of the environmental
  sound in urban places.
\newblock In {\em Euronoise}, 2012.

\bibitem{guastavino2007}
C.~Guastavino.
\newblock Categorization of environmental sounds.
\newblock {\em Can. J. Exp. Psychol.}, 61:54--63, 2007.

\bibitem{gygi2007}
B.~Gygi, G.~R. Kidd, and C.~S. Watson.
\newblock Similarity and categorization of environmental sounds.
\newblock {\em Perception \& Psychophysics}, 69:839--55, 2007.

\bibitem{salamon2014}
J.~Salamon, C.~Jacoby, and J.~P. Bello.
\newblock A dataset and taxonomy for urban sound research.
\newblock In {\em 22nd ACM International Conference on Multimedia}, 2014.

\bibitem{brown2011}
A.L. Brown.
\newblock Towards standardization in soundscape preference assessment.
\newblock {\em Applied Acoustics}, 72:387--392, 2011.

\bibitem{lavandier2006}
C.~Lavandier and B.~Defreville.
\newblock The contribution of sound source characteristics in the assessment of
  urban soundscapes.
\newblock {\em Acta Acust. unit. Acust.}, 92:912--921, 2006.

\bibitem{ricciardi2014}
P.~Ricciardi, P.~Delaitre, C.~Lavandier, F.~Torchia, and P.~Aumond.
\newblock Sound quality indicators for urban places in paris cross-validated by
  {M}ilan data.
\newblock {\em J. Ac. Soc. Am.}, 138:2337--2348, 2014.

\bibitem{hong2017}
J.Y. Hong and J.Y. Jeon.
\newblock Relationship between spatiotemporal variability of soundscape and
  urban morphology in a multifunctional urban area: A case study in {S}eoul,
  {K}orea.
\newblock {\em Building and Environment}, 126:382--95, 2017.

\bibitem{guastavino2006}
C.~Guastavino.
\newblock The ideal urban soundscape: Investigating the sound quality of
  {F}rench cities.
\newblock {\em Acta Acust. unit. Acust.}, 92:945--51, 2006.

\bibitem{ardouin2018}
J.~Ardouin, L.~Charpentier, M.~Lagrange, F.~Gontier, N.~Fortin, J.~Picaut,
  D.~Ecoti\`ere, G.~Guillaume, and C.~Mietlicky.
\newblock An innovative low-cost sensor for urban sound monitoring.
\newblock In {\em INTER-NOISE 2018}, 2018.

\bibitem{mydlarz2017}
C.~Mydlarz, J.~Salamon, and J.P. Bello.
\newblock The implementation of low-cost urban acoustic monitoring devices.
\newblock {\em Applied Acoustics}, 117:207--218, 2017.

\bibitem{cakir2015}
E.~Cakir, T.~Heittola, H.~Huttunen, and T.~Virtanen.
\newblock Polyphonic sound event detection using multi label deep neural
  networks.
\newblock In {\em 2015 International Joint Conference on Neural Networks
  (IJCNN)}, 2015.

\bibitem{salamon2017-2}
J.~Salamon and J.~P. Bello.
\newblock Deep convolutional neural networks and data augmentation for
  environmental sound classification.
\newblock {\em IEEE Signal Processing Letters}, 24, 2017.

\bibitem{lafay2016}
Gr{\'e}goire Lafay, Mathieu Lagrange, Mathias Rossignol, Emmanouil Benetos, and
  Axel Roebel.
\newblock {A morphological model for simulating acoustic scenes and its
  application to sound event detection}.
\newblock {\em {IEEE/ACM Transactions on Audio, Speech and Language
  Processing}}, 24(10):1854--1864, 2016.

\bibitem{salamon2017}
J.~Salamon, D.~MacConnell, M.~Cartwright, P.~Li, and J.~P. Bello.
\newblock Scaper: A library for soundscape synthesis and augmentation.
\newblock In {\em 2017 IEEE Workshop on Applications of Signal Processing to
  Audio and Acoustics (WASPAA)}, 2017.

\bibitem{gloaguen2017}
J.R. Gloaguen, A.~Can, M.~Lagrange, and J.F. Petiot.
\newblock Creation of a corpus of realistic urban sound scenes with controlled
  acoustic properties.
\newblock In {\em Proceedings of Meetings on Acoustics}, 2017.

\bibitem{panayotov2015}
V.~Panayotov, G.~Chen, D.~Povey, and S.~Khudanpur.
\newblock Librispeech: an {ASR} corpus based on public domain audio books.
\newblock In {\em Proceedings of the 2015 IEEE International Conference on
  Acoustics, Speech and Signal Processing (ICASSP)}, 2015.

\bibitem{gontier2018}
F.~Gontier, P.~Aumond, M.~Lagrange, C.~Lavandier, and J.-F. Petiot.
\newblock Towards perceptual soundscape characterization using event detection
  algorithms.
\newblock In {\em Proceedings of the Detection and Classification of Acoustic
  Scenes and Events 2018 workshop (DCASE)}, 2018.

\bibitem{dagnelie2003}
P.~Dagnelie.
\newblock {\em Principes d'exp\'erimentation: planification des exp\'eriences
  et analyse de leurs r\'esultats}.
\newblock Presses Agronomiques de Gembloux, 2003.

\bibitem{wilcoxon1945}
F.~Wilcoxon.
\newblock Individual comparisons by ranking methods.
\newblock {\em Biometrics Bulletin}, 1:80--3, 1945.

\bibitem{pratt1959}
J.~W. Pratt.
\newblock Remarks on zeros and ties in the {W}ilcoxon signed rank procedures.
\newblock {\em Journal of the American Statistical Association}, 54:655--67,
  1959.

\bibitem{itatoolbox2017}
M.~Berzborn, R.~Bomhardt, J.~Klein, J.G. Richter, and M.~Vorlander.
\newblock The ita-toolbox: an open source matlab toolbox for acoustic
  measurements and signal processing.
\newblock In {\em 43th Annual German Congress on Acoustics}, 2017.

\bibitem{gontier2017}
F.~Gontier, M.~Lagrange, P.~Aumond, A.~Can, and C.~Lavandier.
\newblock An efficient audio coding scheme for quantitative and qualitative
  large scale acoustic monitoring using the sensor grid approach.
\newblock {\em Sensors}, 17, 2017.

\bibitem{kingma2015}
D.~P. Kingma and J.~Lei Ba.
\newblock Adam: a method for stochastic optimization.
\newblock In {\em Proceedings of the 2015 International Conference on Learning
  Representations (ICLR)}, 2015.

\end{thebibliography}
